---
title: "TAKEAWAY CAT2"
author: "Patricia Lagat"
date: "7/6/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#QUESTION 1(a)
#We prepared the data by first removing the first rows to remain with the table
```{r}
library(readxl)
CATQ1_monthly <- read_excel("CATQ1_monthly.xlsx")
View(CATQ1_monthly)
myData0<-as.matrix(read_xlsx("CATQ1_monthly.xlsx"))
myData <- myData0[,-1] #To remove the date column"
head(myData)
```
#Cumulative returns
```{r}
Rapple<-myData[,2] #2nd column for Apple
Rgoogle<-myData[,4] #4th column is for Google

Rewp <- 0.5*Rapple + 0.5*Rgoogle #for the equally weighted portfolio
Rewp


cumuRewp<-rep(0,60) #We created an empty vector to hold cumulative return


for(i in 1:60){cumuRewp[i] <- prod(Rewp[1:i])} #Loop through the 60 periods
cumuRewp

plot(1:60, cumuRewp, type= "l") #gives the plot of monthly returns
```

###Question 1(b)
```{r}
CAPM_Apple <- lm(CATQ1_monthly$Apple ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_Apple # Beta = 1.175

CAPM_Ford <- lm(CATQ1_monthly$`Ford Motor` ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_Ford  #Beta =1.203

CAPM_Google <- lm(CATQ1_monthly$Google ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_Google #Beta = 0.9023

CAPM_Kellogg <- lm(CATQ1_monthly$Kellogg ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_Kellogg #Beta=0.5402

CAPM_USsteel<- lm(CATQ1_monthly$`US Steel` ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_USsteel  #Beta = 2.4626

CAPM_Walmart <- lm(CATQ1_monthly$Walmart ~ CATQ1_monthly$Market, CATQ1_monthly)
CAPM_Walmart   #Beta= 0.3706
```
#aggressive stocks are for Apple,US steel
#defensive stocks are Ford Motor,Google, Kellogg, Walmart

###Question 1(c)
#From CATQ3_annual dataset, we extracted the Rf for 2016 to 2020
```{r}
Rf <- mean(c(0.2,0.8,1.81,2.14,0.44)) #riskfree rate average
Rf #1.078

Rm <- mean(CATQ1_monthly$Market) #market return average
Rm #1.198667

ER_A <- Rf + 1.175*(Rm-Rf) #Apple expected return
ER_A  #1.219783

ER_FM <- Rf + 1.203*(Rm-Rf) #Ford Motor
ER_FM  #1.223162

ER_G <- Rf + 0.9023*(Rm-Rf) #Google
ER_G  #1.186878

ER_k <- Rf + 0.5402*(Rm-Rf) #Kellogg
ER_k  #1.219783

ER_US <- Rf + 2.4626*(Rm-Rf) #US Steel
ER_US  #1.375154

ER_W <- Rf + 0.3706*(Rm-Rf)  #Walmart return
ER_W  #1.122719 
```
###QUESTION 2
```{r}
library(readxl)
CATQ3_annual <- read_excel("D:/FAP/CATQ3_annual.xlsx")
View(CATQ3_annual)

Market_Excess <- CATQ3_annual$Market- CATQ3_annual$`Risk-Free`
CAPM_HML <- lm(CATQ3_annual$HML ~ Market_Excess)
summary(CAPM_HML)
```
#the intercept value is 0.047 which is statistically insignificant thus
##We fail to reject the null at 99% confidence interval


